Step 1. Understanding the Business Problem
The company wants to know:

Does the new webpage improve conversion rate?

This is called A/B Testing.

Two versions:

Version A — Control

Existing webpage.

Version B — Treatment

New webpage.

Goal:

Compare:

P(conversion | old page)

vs

P(conversion | new page)

If:

New > Old

→ launch new page.

Otherwise:

→ keep old page.
```{r}
data <- read.csv("C:/Users/jaina/Downloads/ab_data1.csv")
data
```
```{r}
str(data)
```


```{r}
dim(data)
```


```{r}
colSums(is.na(data))
```
```{r}
sum(duplicated(data))
```



```{r}
table(data$group)
```
```{r}
table(data$landing_page)
```


```{r}
table(data$converted)
```


```{r}
mean(data$converted)
```


```{r}
table(data$group,data$converted)
```
```{r}
prop.table(table(data$group,data$converted),1)
```


```{r}
library(ggplot2)
ggplot(data,aes(group))+
geom_bar(fill="steelblue")+
labs(
title="Users per Experimental Group",
x="Group",
y="Count"
)
```
After EDA ask:

Q1

Were groups balanced?

Check:

group counts
landing page counts

We will filter the data based on matching control and treatment groups

```{r}

data <- data %>% mutate(match = (group == "treatment" & landing_page == "new_page") |
                       (group == "control" & landing_page == "old_page"))

data <- data %>% filter(match == TRUE)

```


Basic AB Testing (Old Page)

```{r}

old_page <- data %>% filter(group == "control")
new_page <- data %>% filter(group == "treatment")

alpha = 2
beta = 20

alpha_post <- alpha + sum(old_page$converted)
beta_post <- beta + length(old_page$converted) - sum(old_page$converted)

alpha_post / (alpha_post + beta_post)


```


New Page


```{r}

alpha_post <- alpha + sum(new_page$converted)
beta_post <- beta + length(new_page$converted) - sum(new_page$converted)

alpha_post / (alpha_post + beta_post)

```