Step 1. Understanding the Business Problem
The company wants to know:

Does the new webpage improve conversion rate?

This is called A/B Testing.

Two versions:

Version A — Control

Existing webpage.

Version B — Treatment

New webpage.

Goal:

Compare:

P(conversion | old page)

vs

P(conversion | new page)

If:

New > Old

→ launch new page.

Otherwise:

→ keep old page.
```{r}
data <- read.csv("C:/Users/jaina/Downloads/ab_data1.csv")
data
```
```{r}
str(data)
```


```{r}
dim(data)
```


```{r}
colSums(is.na(data))
```
```{r}
sum(duplicated(data))
```



```{r}
table(data$group)
```
```{r}
table(data$landing_page)
```


```{r}
table(data$converted)
```


```{r}
mean(data$converted)
```


```{r}
table(data$group,data$converted)
```
```{r}
prop.table(table(data$group,data$converted),1)
```


```{r}
library(ggplot2)
ggplot(data,aes(group))+
geom_bar(fill="steelblue")+
labs(
title="Users per Experimental Group",
x="Group",
y="Count"
)
```
After EDA ask:

Q1

Were groups balanced?

Check:

group counts
landing page counts

We will filter the data based on matching control and treatment groups

```{r}

data <- data %>% mutate(match = (group == "treatment" & landing_page == "new_page") |
                       (group == "control" & landing_page == "old_page"))

data <- data %>% filter(match == TRUE)

```

Performing Hypothesis testing where the new page is resonable or not .
Null Hypothesis

New page does not improve conversions.

Alternative Hypothesis

New page performs better.

```{r}
control <- subset(data_clean,
group=="control")

treatment <- subset(data_clean,
group=="treatment")
```


```{r}
x1 <- sum(control$converted)
n1 <- nrow(control)

x2 <- sum(treatment$converted)
n2 <- nrow(treatment)
```


```{r}
prop.test(
c(x1,x2),
c(n1,n2),
alternative="less"
)
```
```{r}
prop.test(
c(x1,x2),
c(n1,n2),
alternative="two.sided"
)
```
After cleaning inconsistent observations and duplicate users, a two-sample proportion test was conducted to compare conversion rates between the control and treatment groups. The control group showed a conversion rate of 12.04%, while the treatment group showed 11.88%. The hypothesis test produced a p-value of 0.9042, which is substantially larger than α = 0.05. Therefore, we fail to reject the null hypothesis and conclude that there is insufficient evidence that the new webpage increases conversion rates. Based on the observed data, the old webpage performed slightly better.Therefore, we fail to reject the null hypothesis and conclude that there is insufficient evidence that the webpages differ in conversion performance.

que2

Testing via bayesian stat .

```{r}
alpha_old <- 2
beta_old <- 20

alpha_new <- 1
beta_new <- 1

```


```{r}

control <- subset(data_clean,
                  group=="control")

treatment <- subset(data_clean,
                    group=="treatment")
```


```{r}
x_old <- sum(control$converted)
n_old <- nrow(control)

x_new <- sum(treatment$converted)
n_new <- nrow(treatment)

```
```{r}
```


```{r}
post_alpha_old <- alpha_old+x_old
post_beta_old <- beta_old+n_old-x_old

post_alpha_new <- alpha_new+x_new
post_beta_new <- beta_new+n_new-x_new
```


```{r}
N <- 100000

samples_old <- rbeta(
N,
post_alpha_old,
post_beta_old)
```


```{r}
samples_new <- rbeta(
N,
post_alpha_new,
post_beta_new)
```
```{r}
```


```{r}
mean(samples_new>samples_old)
```


```{r}
quantile(samples_old,
         c(.025,.975))

quantile(samples_new,
         c(.025,.975))
```
A Bayesian A/B analysis was conducted using independent Beta priors for the conversion rates. A Beta(2,20) prior was specified for the old page based on historical observations, while a weak prior was used for the new page. Posterior distributions were updated using the observed conversion data. The posterior probability that the new page outperforms the old page was estimated as 0.095, indicating only a 9.5% chance that the new webpage achieves a higher conversion rate. The 95% posterior credible interval for the old page was (0.1187, 0.1221), while the interval for the new page was (0.1172, 0.1205). Overall, the Bayesian analysis provides little evidence supporting adoption of the new webpage, and the old page appears more favorable.



Basic AB Testing (Old Page)

```{r}

old_page <- data %>% filter(group == "control")
new_page <- data %>% filter(group == "treatment")

alpha = 2
beta = 20

alpha_post <- alpha + sum(old_page$converted)
beta_post <- beta + length(old_page$converted) - sum(old_page$converted)

alpha_post / (alpha_post + beta_post)


```


New Page


```{r}

alpha_post <- alpha + sum(new_page$converted)
beta_post <- beta + length(new_page$converted) - sum(new_page$converted)

alpha_post / (alpha_post + beta_post)

```
