Step 1. Understanding the Business Problem
The company wants to know:

Does the new webpage improve conversion rate?

This is called A/B Testing.

Two versions:

Version A — Control

Existing webpage.

Version B — Treatment

New webpage.

Goal:

Compare:

P(conversion | old page)

vs

P(conversion | new page)

If:

New > Old

→ launch new page.

Otherwise:

→ keep old page.
```{r}
data <- read.csv("C:/Users/jaina/Downloads/ab_data1.csv")
data
```
```{r}
str(data)
```


```{r}
dim(data)
```


```{r}
colSums(is.na(data))
```
```{r}
sum(duplicated(data))
```



```{r}
table(data$group)
```
```{r}
table(data$landing_page)
```


```{r}
table(data$converted)
```


```{r}
mean(data$converted)
```


```{r}
table(data$group,data$converted)
```
```{r}
prop.table(table(data$group,data$converted),1)
```


```{r}
library(ggplot2)
ggplot(data,aes(group))+
geom_bar(fill="steelblue")+
labs(
title="Users per Experimental Group",
x="Group",
y="Count"
)
```
After EDA ask:

Q1

Were groups balanced?

Check:

group counts
landing page counts


```{r}
```

